A general Nullstellensatz for generalized spaces

### 2019-03-17 paper-qcoh.tex
Better explain the equivalence relation

\begin{thm}\label{thm:definability}
Let~$\TT$ be a geometric theory. Let~$x_1\?X_1,\ldots,x_n\?X_n$ be a context over the
signature of~$\TT$. Then the canonical morphism
\[ \mathrm{Form}^\star_{\vec x}(\ul{\TT}/U_\TT)/(\dashv\vdash_{\vec x}) \longrightarrow P(X_1 \times
\cdots \times X_n) \]
sending, internally speaking, the equivalence class of a geometric$^\star$ formula~$\varphi$ over the
signature of~$\ul{\TT}/U_\TT$ in the context~$\vec x$ to the subset~$\{ (x_1,\ldots,x_n) \,|\, \varphi
\}$ is an isomorphism.
% XXX explain equivalence relation
\end{thm}

>>>>

\begin{thm}\label{thm:definability}
Let~$\TT$ be a geometric theory. Let~$x_1\?X_1,\ldots,x_n\?X_n$ be a context over the
signature of~$\TT$. Let~$\mathrm{Form}^\star_{\vec
x}(\ul{\TT}/U_\TT)/(\dashv\vdash_{\vec x})$ be the~$\Set[\TT]$-object of
geometric$^\star$ formulas over the signature of~$\ul{\TT}/U_\TT$ in the
context~$\vec x$, where any two such formulas are identified if and only
if~$\ul{\TT}/U_\TT$ proves them equivalent.
Then the canonical morphism
\[ \mathrm{Form}^\star_{\vec x}(\ul{\TT}/U_\TT)/(\dashv\vdash_{\vec x}) \longrightarrow P(X_1 \times
\cdots \times X_n) \]
sending, internally speaking, the equivalence class of a geometric$^\star$
formula~$\varphi$ to the subset~$\{ (x_1,\ldots,x_n) \,|\, \varphi \}$ is an isomorphism.
\end{thm}
